Cosmic Web

### 2014-01-21 paper/main.tex
updated table

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the number indicate the same number as a percentage of the
total population. }
\label{table:models}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. }
\label{table:models}
\end{center}
\end{table}
